si: code and prose exploring Spatial Interaction models

### 2022-04-25 README.qmd
Tweak readem

The goal of {si} is to provide a simple, '[tidy](https://dplyr.tidyverse.org/)', and flexible framework for developing spatial interaction models (SIMs), which estimate the amount of movement between spatial entities.

>>>>

The goal of {si} is to provide a simple, [tidy](https://www.tidyverse.org/), and flexible framework for developing spatial interaction models (SIMs).
SIMs estimate the amount of movement between spatial entities and can be used for many things, including to support evidence-based investment in sustainable transport infrastructure and prioritisation of location options for public services.
